Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-14 paper/paper.tex
introduce \PPOBRP{}

\section{Recovering a Perfect Partition}	\label{sec:ppl}
%\subsection{Perfect Partition Model}\label{sec:perfectPartition}
\maciek{Here introduce a restricted model of \PPOBRP{}, the restricted variant where the input sequence can be perfectly partitioned}
\maciek{ every algorithm must colocate every communicating pair.
	\mahmoud{updated!}}
We  focus on a restricted variant of   \PPOBRP{}
where the communication graph can be partitioned into $\ell$ clusters without any inter-cluster edges.
Moreover, we assume an optimal offline algorithm (OPT) moves to this \emph{perfect partition}
at the beginning and stays there permanently.
Then the task of an online algorithm is to "recover" (or learn) the perfect partition while not paying too much more than OPT.
This implies that on a request between any two non-collocated nodes,
any online algorithm must eventually collocate them,
as otherwise it not competitive under a sequence that repeats the same request arbitrarily many times.
Hence,
any competitive algorithm,
must at some point collocate all nodes of a  connected sub-graph of the communication graph.
We refer to this connected sub-graph as a \emph{component}.
An algorithm that always keeps a component collocated is \emph{component-respecting}.
%\maciek{Note that the algorithm from Section~\ref{sec:k3} is $O(\ell)$-competitive for the Perfect Partition Model, as during the first phase, a perfect partition of input exists.}

@@

In this section we show a lower bound of $\Omega(k \cdot \ell)$.
The constructed input sequence allows OPT to move to a perfect partition, and hence
the construction also constitutes a lower bound for \PPOBRP{}.
This complements an upper bound of $O(k \cdot \ell)$
for \PPOBRP{} that we present in Section \ref{sec:ppl}.

>>>>

\section{Recovering a Perfect Partition}	\label{sec:ppl}
%\subsection{Perfect Partition Model}\label{sec:perfectPartition}
\maciek{Here introduce a restricted model of \PPOBRP{}, the restricted variant where the input sequence can be perfectly partitioned}
\maciek{ every algorithm must colocate every communicating pair.
	\mahmoud{updated!}}
We  focus on a restricted variant of  \OBRP{},
where the communication graph can be partitioned into $\ell$ clusters without any inter-cluster edges.
Moreover, we assume an optimal offline algorithm (OPT) moves to this \emph{perfect partition}
at the beginning and stays there permanently.
We refer this variant as \PPOBRP{}.
The task of an online algorithm for \PPOBRP{} is to "recover" (or learn) the perfect partition while not paying too much more than OPT.
This implies that on a request between any two non-collocated nodes,
any online algorithm must eventually collocate them,
as otherwise it not competitive under a sequence that repeats the same request arbitrarily many times.
Hence,
any competitive algorithm,
must at some point collocate all nodes of a  connected sub-graph of the communication graph.
We refer to this connected sub-graph as a \emph{component}.
An algorithm that always keeps a component collocated is \emph{component-respecting}.
%\maciek{Note that the algorithm from Section~\ref{sec:k3} is $O(\ell)$-competitive for the Perfect Partition Model, as during the first phase, a perfect partition of input exists.}

@@

In this section we show a lower bound of $\Omega(k \cdot \ell)$.
The constructed input sequence allows OPT to move to a perfect partition, and hence
the construction also constitutes a lower bound for \OBRP{}.
This complements an upper bound of $O(k \cdot \ell)$
for \PPOBRP{} that we present in Section \ref{sec:ppl}.
